Austria's Covid legislation: Duration of parliamentarian consultation period in comparision.

### 2021-02-16 _post/2020-11-18-recreating-nyt-election-map/recreating-nyt-election-map.Rmd
update nyt map a facebook vienna

---
title: "Recreating NYT election map"
description: |
  How to re-create election maps by the NYT with ggplot
date: 11-18-2020

draft: TRUE

@@

creative_commons: CC BY-NC-SA

---

@@

![](index_files/Capture.PNG)

@@

```{r message=FALSE, warning=FALSE}
library(jsonlite)
library(ggtext)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(sf)
library(patchwork)
library(knitr)
library(svglite)
library(tidyverse)

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=background-color:).*?(?=;)")) %>% str_trim()
```

@@

```{r setup, echo = T}
knit_hooks$set(wrap = function(before, options, envir) {
  if (before) {
    paste0("<", options$wrap, ">")
  } else {
    paste0("</", options$wrap, ">")
  }
})

knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)

@@

<details open>
<summary>Code: Calculate centroids</summary>

@@

sf_cent2 <- sf_cent %>% 
  # left_join(., df_change %>% select(county, party, change_parties, change_vote_absolute) %>% 
  left_join(., df_change %>% 
              # select(county, party, change_parties) %>% 
              mutate(county=stringr::str_to_upper(county)),
            by=c("COUNTY_NAM"="county")) %>% 
  mutate(x_change=diff_change_vote_share*sin(20),
         y_change=abs(diff_change_vote_share)*cos(20)) %>% 
  mutate(point_x_end=point_x+(x_change*scale_factor),
         point_y_end=(y_change*scale_factor)+point_y)
```
</details>

Use the `googleway` package to get the long/lat details for Philly and Pittsburgh (see [here](https://werk.statt.codes/post/primary-schools-in-vienna/){target="_blank"} for another blog where I used the package quite heavily.)

<details open>
<summary>Code: Geocode cities</summary>
```{r message=FALSE, warning=FALSE}
# data for pittsburgh and philadelphia ------------------------------------

library(googleway)
cities <- c("Philadelphia", "Pittsburgh")
df_cities <- map_dfr(cities, ~google_geocode(address=.x, 
                                             key=Sys.getenv("googleway"),
                                             simplify = T))

df_cities_geom <- df_cities$results$geometry$location

df_cities_add <- df_cities$results$formatted_address %>% enframe(., name=NULL, value="city")

df_cities <- bind_cols(df_cities_geom, df_cities_add)

sf_cities <- st_as_sf(df_cities, coords = c("lng", "lat"), remove = FALSE, 
         crs = 4326, agr = "constant") %>% 
  st_transform(32617)
```
</details>

@@

<details open>
<summary>Code: map</summary>
```{r message=FALSE, warning=FALSE}
# plot --------------------------------------------------------------------

pl_map <- ggplot()+
  labs(
    # title = 'The Vote in Battleground States<br>
    #    <span style="color:#606060;font-size:35pt;font-family:Times;">Pennsylvania</span>',
    caption="graph remake: Roland Schmidt|@zoowalk|https://werk.statt.codes\noriginal: https://nyti.ms/3lftRDe"
  )+
  geom_sf(data=pa, 
          size=.1,
          fill="white")+
  geom_sf(data = sf_cities, 
          size=1.5,
          color = 'grey50') +
  geom_sf_text(data = sf_cities,
                aes(label=city %>% 
                      str_extract(., regex("[:alpha:]*"))),
               nudge_y = -10^4.2,
               size=3.2,
               family="Arial",
               color="grey50")+
  geom_segment(data=sf_cent2,
               aes(x=point_x,
                   xend=point_x_end,
                   y=point_y,
                   yend=point_y_end,
                   size=abs(diff_change_vote_absolute),
                   color=party),
               linejoin="mitre",
               arrow=arrow(length=unit(0.2, "cm"),
                           angle=15,
                           type="closed"))+
  scale_x_continuous(expand=expansion(mult=c(.1,.3)))+
  scale_size_continuous(range=c(0,3))+
  scale_color_manual(values=c(democrat="#3f95b0", republican="#ba6b67"))+
  theme_void()+
  theme(plot.background = element_rect(fill=plot_bg_color),
   plot.title = element_markdown(hjust = .5,
                                 lineheight = 3,
                                 color="#606060"
                                 ),
   plot.margin = margin(0,0,0,0, unit="cm"),
   plot.caption = element_text(hjust=0, 
                               family = "Arial",
                               lineheight = 1,
                               color="grey60"),
        legend.position = "none")

```
</details>

```{r echo=FALSE, message=FALSE, warning=FALSE, dev.args=list(bg=plot_bg_color)}
pl_map
```

@@

<details open>
<summary>Code: legend inset</summary>
```{r message=FALSE, warning=FALSE}
# inset -------------------------------------------------------------------

@@

pl_inset <-  df_inset %>% 
ggplot()+
  labs(title="Shift from 2016",
       subtitle="In counties that have reported\n almost all of their votes")+
  geom_segment(aes(x=x,
                   xend=xend,
                   y=y,
                   yend=yend,
                   color=party),
               size=1,
               linejoin="mitre",
               arrow=arrow(length=unit(0.1, "cm"),
                           angle=20,
                           type="closed")
               )+
  geom_text(x=.5, y=-.3, 
            label="More\nRepublican", 
            hjust=0, 
            lineheight=0.8,
            size=3,
            color="grey60", 
            family="Arial")+
  geom_text(x=-.5, y=-.3, label="More\nDemocratic", 
            lineheight=0.8,
            hjust=1, 
            size=3,
            color="grey60", 
            family="Arial")+
  scale_color_manual(values=c(democrat="#3f95b0", republican="#ba6b67"))+
  scale_x_continuous(expand=expansion(ad=c(1,1)), limits=c(-7,7))+
  scale_y_continuous(limits=c(-1,.5), expand=expansion(add=c(0.5, 0.2)))+
  theme_void()+
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5,
                                  family = "Arial",
                                  face="bold",
                                  color="#606060",
                                  margin = margin(b=0, unit="cm"),
                                  size=13),
        plot.subtitle = element_text(hjust=0.5,
                                     margin = margin(t=0.1, unit="cm"),
                                     size=10,
                                     color="grey60",
                                     family = "Arial"))
```
</details>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, dev.args=list(bg=plot_bg_color)}
pl_inset

@@

<details open>
<summary>Code: Combine plots</summary>
```{r message=FALSE, warning=FALSE}
# combine plots -----------------------------------------------------------

@@

```
</details>

@@

```{r echo=FALSE, fig.asp=.6, fig.width=9, message=FALSE, warning=FALSE, dev.args=list(bg=plot_bg_color), out.height="110%"}
pl_combined

>>>>

---
title: "Recreating NYT election map"
description: |
  How to re-create election maps by the NYT with ggplot.
date: 11-18-2020

draft: FALSE

@@

creative_commons: CC BY-NC-SA
---

@@

![](recreating-nyt-election-map_files/images/Capture.PNG)

@@

```{r message=FALSE, warning=FALSE}
library(jsonlite)
library(ggtext)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(sf)
library(patchwork)
library(knitr)
library(svglite)
library(tidyverse)
library(opencage)

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=blog-bg-color:).*?(?=;)")) %>%
  str_trim() %>% 
  str_extract(., regex("^#\\S+"))

@@

```{r setup, echo = F}
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)

@@

<summary>Code: Calculate centroids</summary>

@@

sf_cent2 <- sf_cent %>% 
  # left_join(., df_change %>% select(county, party, change_parties, change_vote_absolute) %>% 
  left_join(., df_change %>% 
              # select(county, party, change_parties) %>% 
              mutate(county=stringr::str_to_upper(county)),
            by=c("COUNTY_NAM"="county")) %>% 
  mutate(x_change=diff_change_vote_share*sin(20),
         y_change=abs(diff_change_vote_share)*cos(20)) %>% 
  mutate(point_x_end=point_x+(x_change*scale_factor),
         point_y_end=(y_change*scale_factor)+point_y)
```

Use the ~~`googleway`~~ `opencage` package to get the long/lat details for Philly and Pittsburgh.[^1]

[^1]: In a previous version I used the googleway package. The opencage package allows to get geolocation without needing to access the google API.

<summary>Code: Geocode cities</summary>

```{r message=FALSE, warning=FALSE, eval=F, include=F}
# data for pittsburgh and philadelphia ------------------------------------

# library(googleway)
# cities <- c("Philadelphia", "Pittsburgh")
# df_cities <- map_dfr(cities, ~google_geocode(address=.x, 
#                                              key=Sys.getenv("googleway"),
#                                              simplify = T)) 
# 
# df_cities_geom <- df_cities$results$geometry$location
# 
# df_cities_add <- df_cities$results$formatted_address %>% enframe(., name=NULL, value="city")
# 
# df_cities <- bind_cols(df_cities_geom, df_cities_add)
# 
# sf_cities <- st_as_sf(df_cities, coords = c("lng", "lat"), remove = FALSE, 
#          crs = 4326, agr = "constant") %>% 
#   st_transform(32617)
```

```{r}
cities <- c("Philadelphia", "Pittsburgh")
df_cities <- map_dfr(cities, ~oc_forward_df(placename=.x))

sf_cities <- st_as_sf(df_cities, coords = c("oc_lng", "oc_lat"), remove = FALSE, 
         crs = 4326, agr = "constant") %>% 
  st_transform(32617)

@@

<summary>Code: map</summary>

```{r message=FALSE, warning=FALSE}
# plot --------------------------------------------------------------------

pl_map <- ggplot()+
  labs(
    # title = 'The Vote in Battleground States<br>
    #    <span style="color:#606060;font-size:35pt;font-family:Times;">Pennsylvania</span>',
    caption="graph remake: Roland Schmidt|@zoowalk|https://werk.statt.codes\noriginal: https://nyti.ms/3lftRDe"
  )+
  geom_sf(data=pa, 
          size=.1,
          fill="white")+
  geom_sf(data = sf_cities, 
          size=1.5,
          color = 'grey50') +
  geom_sf_text(data = sf_cities,
                aes(label=placename %>% 
                      str_extract(., regex("[:alpha:]*"))),
               nudge_y = -10^4.2,
               size=3.2,
               family="Arial",
               color="grey50")+
  geom_segment(data=sf_cent2,
               aes(x=point_x,
                   xend=point_x_end,
                   y=point_y,
                   yend=point_y_end,
                   size=abs(diff_change_vote_absolute),
                   color=party),
               linejoin="mitre",
               arrow=arrow(length=unit(0.2, "cm"),
                           angle=15,
                           type="closed"))+
  scale_x_continuous(expand=expansion(mult=c(.1,.3)))+
  scale_size_continuous(range=c(0,3))+
  scale_color_manual(values=c(democrat="#3f95b0", republican="#ba6b67"))+
  theme_void()+
  theme(plot.background = element_rect(fill=plot_bg_color),
   plot.title = element_markdown(hjust = .5,
                                 lineheight = 3,
                                 color="#606060"
                                 ),
   plot.margin = margin(0,0,0,0, unit="cm"),
   plot.caption = element_text(hjust=0, 
                               family = "Arial",
                               lineheight = 1,
                               color="grey60"),
        legend.position = "none")

```{r echo=FALSE, message=FALSE, warning=FALSE, dev.args=list(bg=glue::glue("{plot_bg_color}")), dev="ragg_png"}
pl_map
```

@@

<summary>Code: legend inset</summary>

```{r message=FALSE, warning=FALSE}
# inset -------------------------------------------------------------------

@@

pl_inset <-  df_inset %>% 
ggplot()+
  labs(title="Shift from 2016",
       subtitle="In counties that have reported\n almost all of their votes")+
  geom_segment(aes(x=x,
                   xend=xend,
                   y=y,
                   yend=yend,
                   color=party),
               size=1,
               linejoin="mitre",
               arrow=arrow(length=unit(0.1, "cm"),
                           angle=20,
                           type="closed")
               )+
  geom_text(x=.5, y=-.3, 
            label="More\nRepublican", 
            hjust=0, 
            lineheight=0.8,
            size=3,
            color="grey60", 
            family="Arial")+
  geom_text(x=-.5, y=-.3, label="More\nDemocratic", 
            lineheight=0.8,
            hjust=1, 
            size=3,
            color="grey60", 
            family="Arial")+
  scale_color_manual(values=c(democrat="#3f95b0", republican="#ba6b67"))+
  scale_x_continuous(expand=expansion(ad=c(1,1)), limits=c(-7,7))+
  scale_y_continuous(limits=c(-1,.5), expand=expansion(add=c(0.5, 0.2)))+
  theme_void()+
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5,
                                  family = "Arial",
                                  face="bold",
                                  color="#606060",
                                  margin = margin(b=0, unit="cm"),
                                  size=13),
        plot.subtitle = element_text(hjust=0.5,
                                     margin = margin(t=0.1, unit="cm"),
                                     size=10,
                                     color="grey60",
                                     family = "Arial"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=2, dev.args=list(bg=glue::glue("{plot_bg_color}")), dev="ragg_png"}
pl_inset

@@

<summary>Code: Combine plots</summary>

```{r message=FALSE, warning=FALSE}
# combine plots -----------------------------------------------------------

@@

@@

```{r echo=FALSE, fig.asp=.6, fig.width=9, message=FALSE, warning=FALSE, dev="ragg_png", dev.args=list(bg=glue::glue("{plot_bg_color}")), out.height="110%", crop=T}
pl_combined

### 2021-02-16 _post/2020-12-19-vienna-elections-2020-analysis-of-parties-ads-on-facebook/welcome.Rmd
update nyt map a facebook vienna

Do I see this text

@@

glimpse(df_ads)

@@

```{r echo=FALSE}
glimpse(df_ads_wide)
```

@@

```{r message=FALSE, warning=FALSE}
df_pl_pages <- df_ads_wide %>% 
  group_by(party) %>% 
  mutate(page_name_lum=fct_lump_n(page_name, n=5,
                                  other_level="all other")) %>% 
  group_by(party, page_name_lum) %>% 
  summarise(ads_n=n(),
            across(.cols=contains("spend_") & where(is.numeric),
                   .fns=sum)) %>% 
  select(party, page_name_lum, ads_n, spend_lower_bound_rev, spend_mid, spend_upper_bound) %>%   ungroup() %>% 
  arrange(-ads_n)

>>>>

@@

@@

@@

```{r message=FALSE, warning=FALSE}
df_pl_pages <- df_ads_wide %>% 
  ungroup() %>% 
  group_by(party) %>% 
  mutate(page_name_lum=fct_lump_n(page_name, n=5,
                                  other_level="all other")) %>% 
  ungroup() %>% 
  group_by(party, page_name_lum) %>% 
  summarise(ads_n=n(),
            across(.cols=c(contains("spend_") & where(is.numeric)),
                   .fns=sum
                   )) %>% 
  ungroup() %>% 
  select(party, page_name_lum, ads_n, spend_lower_bound_rev, spend_mid, spend_upper_bound) %>%   
  arrange(-ads_n)

### 2021-02-16 _post/2021-01-22-covidconsultationduration/covidconsultationduration.Rmd
update format post similarity
update nyt map a facebook vienna

Over New Year (!), the Austrian government introduced another bill with the aim to get a grip on the COVID pandemic. With the speed with which things have been developping and the flurry of hard/soft/de facto lockdowns, I have to confess that I would have to look into the text to recall the changes introduced by bill 88/ME (in full: *'Epidemiegesetz, COVID-19-Maßnahmengesetz, Änderung'*). However, what made the bill remarkable even during these times was its legislative genesis, with the government limiting the public consultative process to only three days. As mentioned in previous posts, Austria's legislative procedure includes a public consultation process which allows citizens, NGOs, churches etc. to file submissions in which they can raise concerns and provide feedback on the draft law. At least in theory, it's a feedback loop which allows the government to solicit input and revise its bills.

@@

This debate made me wonder how long other bills were open for the consultative process and how the bill 88/ME would compare, also when considering their documents' lengths. To answer these questions, I a) extracted from the parliament's website the start and end dates of each bill's consultative period to calculate the length of the consultative process; b) downloaded the text of all pertaining bills and retrieved their number of pages. Putting the length of the consultation process and the length of the bill together should allow to better evaluate the three day notice for the amendment to the epidemic bill.

@@

```{r chunk_3days, code_folding=NULL, include=F}
pl_consolidated <- df_consolidated %>% 
  filter(duration_collected>=0) %>% #remove those with negative duration
  count(duration_collected<=3) %>% 
  janitor::clean_names() %>%
  mutate(duration_3=as_factor(duration_collected_3)) %>% 
  ggplot()+
  labs(title="Number of bills with three or fewer days of consultation period",
       subtitle="Bill 88/ME XXVII amending the 'law on epidemics' was open for consultation for three days. \nHow many other bills had a similar or shorter consultation period?",
       y="Number of bills",
       x="Length of consultation period",
       caption=caption)+
  geom_bar(aes(x=duration_3,
               y=n,
               fill=duration_3),
           stat="identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(x=as.numeric(duration_3)-(.5*.9),
                y=n,
                label=n),
            # position=position_dodge(width=0.9),
            size=10,
            color="grey30",
            vjust=0,
            hjust=0)+
  scale_x_discrete(labels=c("FALSE"="more than 3 days",
                            "TRUE"="3 days or fewer"),
                   expand = expansion(mult=c(0,0.1)))+
  scale_y_continuous(labels=scales::label_comma(),
                     limits=c(0,NA),
                     expand=expansion(mult=c(0,0.1)))+
  scale_fill_manual(values=c("FALSE"="grey30",
                    "TRUE"="orange"))+
  theme_post()+
  theme(legend.position = "none",
        axis.text.x = element_text(color="grey10"),
        axis.title.y = element_text(color="grey30",
                                    angle=90,
                                    vjust=1,
                                    hjust=0),
        axis.title.x = element_blank())
```

@@

To start with, let's have a look at the number of submissions filled during the consultation process per bill. The plot below  shows quite clearly that bills related to Covid triggered record breaking numbers of submissions. Apart from the three latest Covid bills, only the two drafts related to security issues (*'Sicherheitspolizeigesetz'*) with around 9,000 submissions were within a similar level. To get details, hover over the dots. Note that the y-axis is log-scaled to keep the variation among bills with fewer submissions visible.

@@

## Duration of consultation process and length of bills
But what about the initial question? How unusual is it that a bill of three pages length, i.e. bill 88/ME, is open for consultation for only three days? The plot below essentially addresses the question put forward in the introduction. As the orange dot in the graph below highlights, there has never been another bill with three pages and as little as three days of consultation. The next bills in the same page-length category had eight days (among them a bill amending the law on gambling/*Glückspielgesetz*...). So at least from this perspective, our bill in question has been quite an aberration.

@@

Nevertheless, out of the `r nrow(df_consolidated)` bills open for consultation, `r df_consolidated %>% filter(duration_collected>3) %>% nrow()` featured longer consultation periods than three days. There were only `r df_consolidated %>% filter(duration_collected>=0) %>% filter(duration_collected<=3) %>% nrow()` bills with three or fewer days (excluding results with negative duration or incomplete start/end dates, see [here](#wrongdata)).

@@

```{r, fig.height=5, echo=F, code_folding=NULL}
pl_consolidated
```

## Overview table {#datatable}
If you are interested in the details pertaining to each bill, the table below provides them.

>>>>

Over New Year (!), the Austrian government introduced another bill with the aim to get a grip on the COVID pandemic. With the speed with which things have been developping and the flurry of hard/soft/de facto lockdowns, I have to confess that I would have to look into the text to recall the changes introduced by bill 88/ME (XXVII) (in full: *'Epidemiegesetz, COVID-19-Maßnahmengesetz, Änderung'*). However, what made the bill memorable even during these times was its legislative genesis, with the government limiting the public consultative process to only three days. As mentioned in previous posts, Austria's legislative procedure includes a public consultation process which allows citizens, NGOs, churches etc. to file submissions in which they can raise concerns and provide feedback on the draft law. At least in theory, it's a feedback loop which allows the government to solicit input and revise its bills.

@@

This debate made me wonder how long other bills were open for the consultative process and how bill 88/ME (XXVII) would compare, also when considering their documents' lengths. To answer these questions, I a) extracted from the parliament's website the start and end dates of all bill's consultative period since 1975, *as published on the parliament's website*. Based on these dates I calculated the length of the consultative process; b) downloaded the text of all pertaining bills and retrieved their number of pages. Putting the length of the consultation process and the length of the bill together should allow to better evaluate the three day notice for the amendment to the epidemic bill.

@@

```{r chunk_3days, code_folding=NULL, include=F}
pl_consolidated <- df_consolidated %>% 
  filter(duration_collected>=0) %>% #remove those with negative duration
  count(duration_collected<=3) %>% 
  janitor::clean_names() %>%
  mutate(duration_3=as_factor(duration_collected_3)) %>% 
  ggplot()+
  labs(title="Number of bills with three or fewer days of consultation period",
       subtitle="Bill 88/ME XXVII amending the 'law on epidemics' was open for consultation for three days. \nHow many other bills had a similar or shorter consultation period?",
       y="Number of bills",
       x="Length of consultation period",
       caption=glue::glue("{caption}\nAnalysis excluded {nrow(df_duration_mult %>% filter(if_any(starts_with('date'), is.na)))+nrow(df_duration_collected %>% 
  filter(duration_collected<0))} bills with errors in the data source. See blog for details.")
       )+
  geom_bar(aes(x=duration_3,
               y=n,
               fill=duration_3),
           stat="identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(x=as.numeric(duration_3)-(.5*.9),
                y=n,
                label=n),
            # position=position_dodge(width=0.9),
            size=10,
            color="grey30",
            vjust=0,
            hjust=0)+
  scale_x_discrete(labels=c("FALSE"="more than 3 days",
                            "TRUE"="3 days or fewer"),
                   expand = expansion(mult=c(0,0.1)))+
  scale_y_continuous(labels=scales::label_comma(),
                     limits=c(0,NA),
                     expand=expansion(mult=c(0,0.1)))+
  scale_fill_manual(values=c("FALSE"="grey30",
                    "TRUE"="orange"))+
  theme_post()+
  theme(legend.position = "none",
        axis.text.x = element_text(color="grey10"),
        axis.title.y = element_text(color="grey30",
                                    angle=90,
                                    vjust=1,
                                    hjust=0),
        axis.title.x = element_text(color="grey30",
                                    # angle=90,
                                    # vjust=1,
                                    hjust=0))

@@

To start with, let's have a look at the number of submissions filed during the consultation process per bill. The plot below  shows quite clearly that bills related to Covid triggered record breaking numbers of submissions. Apart from the three latest Covid bills, only the two drafts related to security issues (*'Sicherheitspolizeigesetz'*) with around 9,000 submissions were within a similar level. To get details, hover over the dots. Note that the y-axis is log-scaled to keep the variation among bills with fewer submissions visible.

@@

## Duration of consultation process and length of bills
But what about the initial question? How unusual is it that a bill of three pages length, i.e. bill 88/ME (XXVII), is open for consultation for only three days? The plot below addresses this question. As the orange dot in the graph below highlights, there has never been another bill with three pages and as little as three days of consultation. The next bills in the same page-length category had eight days (among them a bill amending the law on gambling/*Glückspielgesetz*...). So at least from this perspective, the consultation period for bill 88/ME was quite an aberration.

@@

Nevertheless, out of the `r nrow(df_consolidated)` bills open for consultation, `r df_consolidated %>% filter(duration_collected>3) %>% nrow()` featured longer consultation periods than three days. There were only `r df_consolidated %>% filter(duration_collected>=0) %>% filter(duration_collected<=3) %>% nrow()` bills with three or fewer days (excluding results with negative duration or incomplete start/end dates due to errors in the data source, see [here](#wrongdata)).

@@

```{r, fig.height=5, echo=F, code_folding=NULL, dev="ragg_png"}
pl_consolidated
```

## Overview table {#datatable}
If you are interested in the details pertaining to each bill, the table below provides them. Note that for the sake of completeness this table also includes those bills for which I retrieved impossible/wrong duration data (see [here](#wrongdata) for details.) However, the latter were excluded from the analysis.
